%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Tesla Motors Inc.} % Organization
    {Palo Alto, CA} % Location
    {Jun. 2021 - Jun. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented the majority of a distributed system infrastructure for hardware testing in production environments, utilizing goLang, Python, RabbitMQ, and gRPC. Being used by hundreds of testers worldwide (running 10k+ tests daily) with improvements in development and license costs of 60\% compared previous solutions.}
        \item {Saved over 40\% in development costs by leading the transition of legacy software stacks to distributed system. Documented and standardized the interface so test engineers can transition their test scripts to new system, leading to infrastructure being used by 10+ unique testers within the organization.}
        \item {Continuously improved the architecture since launch. Adding features and meeting new user (test engineers and operators) requirements to expand use cases and scalability.}
        \item {Improved speed (15\%) and readability of database queries on python backend of by utilizing SQLAlchemy library, parallelizing SQL inserts, and utilizing Redis for caching.}
        \item {Wrote C++ drivers for embedded systems that simulate audio signals to meet test requirements for audio drivers systems. Deployed and used in testing thousands of PCBs daily worldwide.}
        \item {Aided in the development of CI/CD pipelines using Github Actions, Ansible, Docker and Kubernetes in the majority of software repos within team. Drastically reduced deployment time (20\%) due to extensive automation of processes.}
%        \item {Refactored and merged two large (10k+ lines) monolithic Python test applications to reduce redundant work within the organization. Led to a reduction of 60\% software engineers, allowing prioritization of other projects.}        
        \item {Helped transition relational database (SQLPostgres) to a No-SQL solution (MongoDB) for more efficient storage of unstructured test data which improved application performance by 10\%.}
        \item {Mentored and onboarded three junior engineers by promoting best practices and knowledge sharing within the team.}
 	   \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Firmware Engineer Internship} % Job title
    {Critical Link LLC} % Organization
    {Syracuse, NY} % Location
    {Jan. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created software infrastructure for testing linux software releases for embedded system using Jenkins jobs with raspberry-pi workers running bas scripts that tested releases on real hardware as part of firmware. Improving automation process of new }
        \item {Altered C code of linux kernels to add boot support of flattened image trees. Reduced the size of boot-loaders by 10MBs and improved scalability of different linux builds.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
